Network Origins of Social Distinction

### 2025-08-17 manuscript.tex
Updates from Overleaf

\subsubsection{Distinction in the Star Graph}
Figure~\ref{fig:star} shows a star graph of order seven where node 1 is the central node connected to six peripheral nodes, who themselves have no other connections. This hub-spoke system is the simplest for exploring the linkages between distinction, status, and constraint. The reason for that is that, for the star node 1, $\kappa_i$ is always equal to zero. In other words, the star node has a minimum network constraint, given that the node-deleted subgraph obtained by removing the central node from the star graph is a disconnected, empty graph, where the status of the peripheral nodes collapses to zero, meaning that the star node's distinction score reduces to:

@@

\subsubsection{Distinction in the Circle and Clique Graphs}

@@

@@

@@

\begin{figure}
    \captionsetup[subfigure]{font=footnotesize,labelfont=footnotesize}
    \centering
     \begin{subfigure}[b]{0.35\textwidth}
        \includegraphics[width=1.0\textwidth]{Plots/Toys/sf.png}
            \caption{Structural Fold}
            \label{fig:sf}
    \end{subfigure} 
    \begin{subfigure}[b]{0.35\textwidth}
        \includegraphics[width=1.0\textwidth]{Plots/Toys/intra.png}
            \caption{2-Connected Subgraphs}
            \label{fig:intra}
    \end{subfigure}
    \begin{subfigure}[b]{0.35\textwidth}
        \includegraphics[width=1.0\textwidth]{Plots/Toys/inter.png}
            \caption{2-Connected Subgraphs with Long Tie}
            \label{fig:inter}
    \end{subfigure}
    \begin{subfigure}[b]{0.35\textwidth}
        \includegraphics[width=1.0\textwidth]{Plots/Toys/wheel.png}
            \caption{Wheel Graph}
            \label{fig:wheel}
    \end{subfigure}
    \label{fig:struct-folds}
    \caption{Distinction Centrality in toy graphs. Nodes with the highest distinction are shown in red, nodes with positive distinction are shown in blue, nodes with negative distinction are shown in tan, and nodes with distinction close to zero are shown in purple.}
\end{figure}

>>>>

\subsubsection{Maximum Inequality and Equality in Distinction}
Figure~\ref{fig:star} shows a star graph of order seven where node 1 is the central node connected to six peripheral nodes, who themselves have no other connections. This hub-spoke system is the simplest for exploring the linkages between distinction, status, and constraint. The reason for that is that, for the star node 1, $\kappa_i$ is always equal to zero. In other words, the star node has a minimum network constraint, given that the node-deleted subgraph obtained by removing the central node from the star graph is a disconnected, empty graph, where the status of the peripheral nodes collapses to zero, meaning that the star node's distinction score reduces to:

@@

@@

%https://journals.aps.org/pre/abstract/10.1103/PhysRevE.71.056103

@@

\begin{figure}
    \captionsetup[subfigure]{font=footnotesize,labelfont=footnotesize}
    \centering
     \begin{subfigure}[b]{0.35\textwidth}
        \includegraphics[width=1.0\textwidth]{Plots/Toys/sf.png}
            \caption{Inter-Group Brokerage}
            \label{fig:sf}
    \end{subfigure} 
     \begin{subfigure}[b]{0.35\textwidth}
        \includegraphics[width=1.0\textwidth]{Plots/Toys/sf.png}
            \caption{Structural Fold}
            \label{fig:sf}
    \end{subfigure} 
    \label{fig:classicbrokerage}
    \caption{Comparison of betweenness brokerage and a structural fold goes here}
\end{figure}

\begin{figure}
    \captionsetup[subfigure]{font=footnotesize,labelfont=footnotesize}
    \centering
     \begin{subfigure}[b]{0.35\textwidth}
        \includegraphics[width=1.0\textwidth]{Plots/Toys/sf.png}
            \caption{Structural Fold}
            \label{fig:sf}
    \end{subfigure} 
    \begin{subfigure}[b]{0.35\textwidth}
        \includegraphics[width=1.0\textwidth]{Plots/Toys/intra.png}
            \caption{2-Connected Subgraphs}
            \label{fig:intra}
    \end{subfigure}
    \begin{subfigure}[b]{0.35\textwidth}
        \includegraphics[width=1.0\textwidth]{Plots/Toys/inter.png}
            \caption{2-Connected Subgraphs with Long Tie}
            \label{fig:inter}
    \end{subfigure}
    \begin{subfigure}[b]{0.35\textwidth}
        \includegraphics[width=1.0\textwidth]{Plots/Toys/wheel.png}
            \caption{Wheel Graph}
            \label{fig:wheel}
    \end{subfigure}
    \label{fig:struct-folds}
    \caption{Examples of varying parameters of mediator brokerage (Burt brokerage). Distinction Centrality in toy graphs. Nodes with the highest distinction are shown in red, nodes with positive distinction are shown in blue, nodes with negative distinction are shown in tan, and nodes with distinction close to zero are shown in purple.}
\end{figure}

\begin{figure}
    \captionsetup[subfigure]{font=footnotesize,labelfont=footnotesize}
    \centering
     \begin{subfigure}[b]{0.35\textwidth}
        \includegraphics[width=1.0\textwidth]{Plots/Toys/sf.png}
            \caption{Structural Fold}
            \label{fig:sf}
    \end{subfigure} 
    \begin{subfigure}[b]{0.35\textwidth}
        \includegraphics[width=1.0\textwidth]{Plots/Toys/intra.png}
            \caption{2-Connected Subgraphs}
            \label{fig:intra}
    \end{subfigure}
    \begin{subfigure}[b]{0.35\textwidth}
        \includegraphics[width=1.0\textwidth]{Plots/Toys/inter.png}
            \caption{2-Connected Subgraphs with Long Tie}
            \label{fig:inter}
    \end{subfigure}
    \begin{subfigure}[b]{0.35\textwidth}
        \includegraphics[width=1.0\textwidth]{Plots/Toys/wheel.png}
            \caption{Wheel Graph}
            \label{fig:wheel}
    \end{subfigure}
    \label{fig:struct-folds}
    \caption{Examples of varying degrees of connectedness within welded subgraphs. Distinction Centrality in toy graphs. Nodes with the highest distinction are shown in red, nodes with positive distinction are shown in blue, nodes with negative distinction are shown in tan, and nodes with distinction close to zero are shown in purple.}
\end{figure}

@@
